---
title: "Demonstration"

output:
  bookdown::html_document2:
    code_folding: hide
    number_sections: false
    
bibliography: ["refs.bib", "r-packages.bib"]
csl: "apa.csl" # try swapping with "nature.csl"
link-citations: true
---

```{r setup, include=FALSE}
# load packages ---------------------------------------------------------------

# packages for reproducibility
library(renv) # creates a snapshot of all the R packages and their versions in this project
#source("R/holepunch.R") # creates a browser-based docker session to add to GH repo

# packages for data science
library(dplyr)   # for manipulating data
library(ggplot2) # for plotting
library(english) # for turning numbers into words
library(kableExtra) # for nice tables

# custom scripts
source("R/simulate.R") # for simulating data
source("R/print.R")      # for printing result in APA format
```

## Methods

### Participants

```{r simulate-data}
# set seed for random number generation
set.seed(42)
# simulate data for a balanced independent t-test
df <- simulate_data(n = 100, mean_1 = 75, mean_2 = 130)
```

```{r participant-info}
# get number of participants in study
n <- nrow(df)
# get number of participants in each group
n_group_a <- count(df, IV) %>% filter(IV == "A") %>% pull(n)
n_group_b <- count(df, IV) %>% filter(IV == "B") %>% pull(n)
```

> There were `` `r knitr::inline_expr("as.character(english(n))")` `` participants in the study, with `` `r knitr::inline_expr("n_group_a")` `` participants in Group A, and participants `` `r knitr::inline_expr("n_group_a")` `` in Group B.

There were `r as.character(english(n))` participants in the study, with `r n_group_a` participants in Group A, and participants `r n_group_b` in Group B.

## Results

### t-test

```{r descriptives}
# get mean and sd
descriptives <- df %>%
  group_by(IV) %>%
  summarise(mean = sprintf("%.2f",mean(DV)),
            sd   = sprintf("%.2f",sd(DV)))
# filter by group
descriptives_a <- filter(descriptives, IV == "A")
descriptives_b <- filter(descriptives, IV == "B")
```

```{r ttest}
# run a t-test
result <- t.test(DV ~ IV, data = df)
```

> An independent t-test was used to test whether there were statistical differences between Group A (\$M = `` `r knitr::inline_expr("pull(descriptives_a, mean)")` ``\$, \$SD = `` `r knitr::inline_expr("pull(descriptives_a, sd)")` ``\$) and Group B (\$M = `` `r knitr::inline_expr("pull(descriptives_b, mean)")` ``\$, \$SD = `` `r knitr::inline_expr("pull(descriptives_b, sd)")` ``\$). The results of the t-test were: `` `r knitr::inline_expr("print_t.test(result)")` ``.

An independent t-test was used to test whether there were statistical differences between Group A ($M = `r pull(descriptives_a, mean)`$, $SD = `r pull(descriptives_a, sd)`$) and Group B ($M = `r pull(descriptives_b, mean)`$, $SD = `r pull(descriptives_b, sd)`$). The results of the t-test were, `r print_t.test(result)`, which can be seen on Figure\ \@ref(fig:plot).

```{r plot, fig.cap = "A numbered figure with a caption. Cool!"}
ggplot(df, aes(x = IV, y = DV)) +
  geom_bar(stat = "summary", fun = "mean", color = "black", fill = "grey") +
  geom_errorbar(stat = "summary", fun.data = mean_se, width = 0.66) +
  theme_classic()
```

### Reproducibility Statement

> The analyses in this paper were done using `` `r knitr::inline_expr("R.version.string")` ``.

The analyses in this paper were done using `r R.version.string`, and the `stats` R package [@R-base]. This paper was written in R Markdown [@R-rmarkdown] and knitted with `knitr` [@R-knitr]. A full list of packages used in this paper can be seen in Table\ \@ref(tab:packages).

```{r packages, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
# read renv.lock
renvLock <- jsonlite::read_json("renv.lock")
# write R packages from renv.lock to r-packages.bib
knitr::write_bib(names(renvLock$Packages), "r-packages.bib")
# get location of package versions and sources
pkg_version <- paste0("renvLock$Packages$", names(renvLock$Packages), "$Version")
pkg_source <- paste0("renvLock$Packages$", names(renvLock$Packages), "$Repository")

# create tibble of packages, their versions, and their source
pkg_df <- tibble::tibble(
  package = names(renvLock$Packages),
  version = sapply(pkg_version, function(x) eval(parse(text = x))),
  source = sapply(pkg_source, function(x) eval(parse(text = x)))
)
# print table
pkg_df %>%
  kbl(caption = "All packages used in this paper.") %>%
  kable_styling() %>%
  scroll_box(height = "250px")
```

## References
